---
title: "MetaPipeX_Computations_Example"
author: "Jens Fuenderich"
date: "2022-12-04"
output: pdf_document
---

#### Prepare Environment for Example

```{r setup}

## load/install packages, including MetaPipeX (from github)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(magrittr, osfr, readr, stats)
pacman::p_load_gh("JensFuenderich/MetaPipeX/R-Package")

## set up output folder 
# define output path (set to working directory) 
custom_output_path <- getwd() 
# define path for output folder
output_folder_path <- paste(custom_output_path, "MetaPipeX_Output", sep = "/")
# create folder
dir.create(output_folder_path)

```

#### Documenting:

#### Item Data

Creating a folder 0_Item_Data and storing data in that folder.

```{r documenting item data}

## download data from osf (to output_folder_path)
# define path to folder
folder_path <- paste(output_folder_path, "0_Item_Data", sep = "/")
# create folder
dir.create(folder_path)
# download 
RRR4_data_path <- osfr::osf_retrieve_file("t3mns") %>%
  osfr::osf_download(., path = folder_path)
Dang_data_path <- osfr::osf_retrieve_file("8egc5") %>%
  osfr::osf_download(., path = folder_path)

## import data from folder
Item_Level_RRR4 <- readr::read_csv(RRR4_data_path$local_path)

```

#### Computational Step 2:

#### Creating Individual Participant Data (IPD)

Selecting relevant columns & recoding group indication. Applying data cleaning.

```{r step 2}

## select relevant columns 
IPD_RRR4 <- data.frame(MultiLab =  rep("RRR4", 
                                       times = length(Item_Level_RRR4$Site)), 
                       ReplicationProject = rep("Sripada", 
                                                times = length(Item_Level_RRR4$Site)), 
                       Replication = Item_Level_RRR4$Site , 
                       DV = Item_Level_RRR4$ExGauss.I.RTVar.MSIT, 
                       Group = base::ifelse(Item_Level_RRR4$Task == "H", 
                                            yes = 1, 
                                            no = base::ifelse(
                                              Item_Level_RRR4$Task == "E", 
                                              yes = 0, 
                                              no = NA)),
                       Exclusion = Item_Level_RRR4$Exclusions)

## apply data cleaning 
IPD_RRR4 <- base::subset(IPD_RRR4, IPD_RRR4$Exclusion == 1)

```

#### Computational Steps 3-6:

##### Creating Individual Participant Data (IPD)

##### Creating Replication-Level Data

##### Creating Replication-Level Data (merged)

##### Creating Meta-Level Data

##### Creating MetaPipeX Data

#### Documenting:

#### Item Data

Creating the folders\
1_Individual_Participant_Data\
2_Replication_Summaries\
3_Merged_Replication_Summaries\
4_Meta_Analyses\
5_Meta_Pipe_X   and storing data in those folders.

```{r steps 3-6 & documenting}

MetaPipeX_RRR4 <- MetaPipeX::full_pipeline(data = IPD_RRR4, 
                                           output_path = paste(custom_output_path, 
                                                               "/", 
                                                               sep = ""), 
                                           folder_name = "MetaPipeX_Output")
# The MetaPipeX function usually creates a folder as its output, 
# but we are directing it to one that already exists. That way all information 
# from this script is stored in "MetaPipeX_Output". The function should return a
# Warning: 'data_path' already exists 

```

#### Run App

```{r app}

MetaPipeX::ShinyApp()

```
