---
title: "MetaPipeX_stepwise_Computations_Example"
author: "Jens Fuenderich"
date: "2022-12-04"
output: pdf_document
---

#### Prepare Environment for Example

```{r setup}

## load/install packages, including MetaPipeX (from github)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(magrittr, osfr, readr, stats)
pacman::p_load_gh("JensFuenderich/MetaPipeX/R-Package")

## set up output folder 
# define output path (set to working directory) 
custom_output_path <- getwd() 
# define path for output folder
output_folder_path <- paste(custom_output_path, "MetaPipeX_Output", sep = "/")
# create folder
dir.create(output_folder_path)

```

#### Documenting:

##### Item Data

Creating a folder 0_Item_Data and storing data in that folder.

```{r documenting item data}

## download data from osf (to output_folder_path)
# define path to folder
folder_path_item <- paste(output_folder_path, "0_Item_Data", sep = "/")
# create folder
dir.create(folder_path_item)
# download 
RRR4_data_path <- osfr::osf_retrieve_file("t3mns") %>%
  osfr::osf_download(., path = folder_path_item)
Dang_data_path <- osfr::osf_retrieve_file("8egc5") %>%
  osfr::osf_download(., path = folder_path_item)

## import data from folder
Item_Level_RRR4 <- readr::read_csv(RRR4_data_path$local_path)

```

#### Computational Step 2:

##### Creating Individual Participant Data (IPD)

Selecting relevant columns & recoding group indication. Applying data cleaning.

```{r step 2}

## select relevant columns 
IPD_RRR4 <- data.frame(MultiLab =  rep("RRR4", 
                                       times = length(Item_Level_RRR4$Site)), 
                       ReplicationProject = rep("Sripada", 
                                                times = length(Item_Level_RRR4$Site)), 
                       Replication = Item_Level_RRR4$Site , 
                       DV = Item_Level_RRR4$ExGauss.I.RTVar.MSIT, 
                       Group = base::ifelse(Item_Level_RRR4$Task == "H", 
                                            yes = 1, 
                                            no = base::ifelse(
                                              Item_Level_RRR4$Task == "E", 
                                              yes = 0, 
                                              no = NA)),
                       Exclusion = Item_Level_RRR4$Exclusions)

## apply data cleaning 
IPD_RRR4 <- base::subset(IPD_RRR4, IPD_RRR4$Exclusion == 1)

```

#### Documenting:

##### Individual Participant Data (IPD)

Creating a folder 0_Item_Data and storing data in that folder.

```{r documenting ipd}

## document data & download codebook 
# define path to folder
folder_path_ipd <- paste(output_folder_path, "1_Individual_Participant_Data", sep = "/")
# create folder
dir.create(folder_path_ipd)
# export data 
readr::write_csv(IPD_RRR4, paste(folder_path_ipd, "RRR4.csv", sep = "/"))
# download codebook 
readr::write_csv(readr::read_csv(url("https://raw.githubusercontent.com/JensFuenderich/MetaPipeX/main/Supplementary_Material/Table_Templates/1_Individual_Participant_Data/codebook_for_individual_participant_data.csv")), 
                 paste(folder_path_ipd, "codebook_for_individual_participant_data.csv", sep = "/"))

```

#### Computational Step 3:

##### Creating Replication-Level Data (Replication Summaries)

#### Documenting:

2_Replication_Summaries\
and storing data in the folder.

```{r step 3 & documenting replication summaries}

# define path to folder
folder_path_rep_sum <- paste(output_folder_path, 
                             "2_Replication_Summaries/", 
                             sep = "/")
# create folder
dir.create(folder_path_rep_sum)

# apply MetaPipeX function
Replication_Summaries_RRR4 <- MetaPipeX::create_replication_summaries(
  data = IPD_RRR4, 
  output_folder = folder_path_rep_sum)

```

#### Computational Step 4:

##### Creating Replication-Level Data (merged)

#### Documenting:

3_Merged_Replication_Summaries\
and storing data in the folder.

```{r step 4 & documenting merged replication summaries}

# define path to folder
folder_path_m_rep_sum <- paste(output_folder_path, 
                               "3_Merged_Replication_Summaries/", 
                               sep = "/")
# create folder
dir.create(folder_path_m_rep_sum)

## combine into single data set
Merged_Replication_Summaries_RRR4 <- MetaPipeX::merge_replication_summaries(
  data = Replication_Summaries_RRR4$Replication_Summaries,
  output_folder = folder_path_m_rep_sum)

```

#### Computational Step 5:

##### Creating Meta-Level Data

#### Documenting:

4_Meta_Analyses\
and storing data in the folder.

```{r step 5 & documenting meta-level data}

# define path to folder
folder_path_meta_analyses <- paste(output_folder_path, 
                                   "4_Meta_Analyses/", 
                                   sep = "/")
# create folder
dir.create(folder_path_meta_analyses)

## run meta-analyses
Meta_Analyses <- MetaPipeX::meta_analyses(
  data = Merged_Replication_Summaries_RRR4$Merged_Replication_Summaries, 
  output_folder = folder_path_meta_analyses)

```

#### Computational Step 6:

##### Creating Creating MetaPipeX Data

#### Documenting:

5_Meta_Pipe_X\
and storing data in the folder.

```{r step 6 & documenting MetaPipeX data}

## step 6

# define path to folder
folder_path_MetaPipeX <- paste(output_folder_path, 
                                   "5_Meta_Pipe_X/", 
                                   sep = "/")
# create folder
dir.create(folder_path_MetaPipeX)

## combine replication- & meta-level data 

# reorder data frames
merged_replication_summaries <- dplyr::arrange(
  Merged_Replication_Summaries_RRR4$Merged_Replication_Summaries, 
  ReplicationProject)
meta_analyses <- dplyr::arrange(
  Meta_Analyses$Meta_Analyses, 
  ReplicationProject)

# number of replications per replication project 
# (= "How many labs are in each replication project?")
k_per_ReplicationProject <- merged_replication_summaries %>%
  dplyr::count(.,ReplicationProject) %>%
  dplyr::pull(.,n)

# duplication vector (indicates how often replication level column needs to be 
# repeated to match the replication level structure)
duplications <- rep(1:nrow(meta_analyses), k_per_ReplicationProject)

# expand df
expanded_MA <- meta_analyses[duplications,]

# reorder both data frames (so they match) and 
# combine them to create the MetaPipeX App data format
MetaPipeX_Data <- cbind(merged_replication_summaries, expanded_MA)

# add "Replication__Result__" to all lab related columns and 
# "MA__" to all meta-analysis columns
# Replication columns from "T_N" to "SE_SMD"
first_replication_col <- base::which(names(MetaPipeX_Data) == "T_N")
last_replication_col <- base::which(names(MetaPipeX_Data) == "SE_SMD")
names(MetaPipeX_Data)[first_replication_col:last_replication_col] <- paste(
  "Replication__Result__", 
  names(MetaPipeX_Data[,first_replication_col:last_replication_col]), 
  sep = "")

# MA
first_replication_MA <- last_replication_col + 1
last_replication_MA <- ncol(MetaPipeX_Data)
names(MetaPipeX_Data)[first_replication_MA:last_replication_MA] <- paste(
  "MA__", 
  names(MetaPipeX_Data[,first_replication_MA:last_replication_MA]), 
  sep = "")

# delete duplicate/redundant columns
MetaPipeX_Data$MA__MultiLab <- NULL
MetaPipeX_Data$MA__ReplicationProject <- NULL
base::rownames(MetaPipeX_Data) <- NULL


## documenting MetaPipeX data & codebook 

# export data 
readr::write_csv(MetaPipeX_Data, paste(folder_path_MetaPipeX, "MetaPipeX_Data.csv", sep = "/"))
# download codebook 
readr::write_csv(readr::read_csv(url("https://raw.githubusercontent.com/JensFuenderich/MetaPipeX/main/Supplementary_Material/Table_Templates/5_MetaPipeX/codebook_for_meta_pipe_x_data.csv")), 
                 paste(folder_path_MetaPipeX, "codebook_for_meta_pipe_x.csv", sep = "/"))

```

#### Run App

```{r }

MetaPipeX::ShinyApp()

```
